Cycles of the logistic map

### 2013-05-08 doc/pc.tex
add scripts in the data directory
improve prd.ma

\begin{remark}[1]
The M\"obius function $\mu(n)$ is $(-1)^k$
  if $n$ is the product of $k$ distinct primes,
  or 0 if $n$ is divisible by a square of a prime.
$\mu(n)$ = 1, $-1$, $-1$, 0, $-1$, 1, \ldots, starting from $n = 1$.
The $\mu(n)$ is useful for inversion:
$g(n) = \sum_{d|n} \mu(n/d) \, h(d)$
if and only if $h(n) = \sum_{d|n} g(d)$
\cite{hardy}.
\end{remark}

\begin{remark}[2]
$B_{d,c}\Rlam$ is a polynomial of $\lambda$.
Despite the argument $\lambda^{1/c}$,
  the product $\prod_{k=1}^c A_d(R, e^{2k\pi i/c} \lambda^{1/c})$
  is free from radicals of powers of $\lambda^{1/c}$,
  for it is invariant under $\lambda \rightarrow e^{2\pi i} \lambda$;
and $\deg_\lambda B_{d,c}\Rlam = \deg_\lambda A_d\Rlam$.
Particularly, $B_{n,1}\Rlam = A_n\Rlam$.
\end{remark}

@@

\bibitem{brown3}
  A. Brown,
  Solutions of period three for a non-linear difference equation,
  \textit{J. Austral. Math. Soc. Ser. B}
  \textbf{25},
  451--462
  (1984);
%\bibitem{brown4} A. Brown,
  Solutions of period four for a non-linear difference equation,
  %\textit{J. Austral. Math. Soc. Ser. B}
  \textit{ibid.}
  \textbf{26},
  146--164
  (1984).

>>>>

\begin{remark}[1]
Here, ``minimal'' means that the polynomial contains all zeros;
  it does not, however, necessarily mean that the polynomial is irreducible.
\end{remark}

\begin{remark}[2]
The M\"obius function $\mu(n)$ is $(-1)^k$
  if $n$ is the product of $k$ distinct primes,
  or 0 if $n$ is divisible by a square of a prime.
$\mu(n)$ = 1, $-1$, $-1$, 0, $-1$, 1, \ldots, starting from $n = 1$.
The $\mu(n)$ is useful for inversion:
$g(n) = \sum_{d|n} \mu(n/d) \, h(d)$
if and only if $h(n) = \sum_{d|n} g(d)$
\cite{hardy}.
\end{remark}

\begin{remark}[3]
$B_{d,c}\Rlam$ is a polynomial of $\lambda$.
Despite the argument $\lambda^{1/c}$,
  the product $\prod_{k=1}^c A_d(R, e^{2k\pi i/c} \lambda^{1/c})$
  is free from radicals of powers of $\lambda^{1/c}$,
  for it is invariant under $\lambda \rightarrow e^{2\pi i} \lambda$;
and $\deg_\lambda B_{d,c}\Rlam = \deg_\lambda A_d\Rlam$.
Particularly, $B_{n,1}\Rlam = A_n\Rlam$.
\end{remark}

@@

\bibitem{brown3}
  A. Brown,
  Solutions of period three for a non-linear difference equation,
  \textit{J. Austral. Math. Soc. Ser. B}
  \textbf{25},
  451--462
  (1984);

  Solutions of period four for a non-linear difference equation,
  %\textit{J. Austral. Math. Soc. Ser. B}
  \textit{ibid.}
  \textbf{26},
  146--164
  (1984).
